### 2015-04-29 Docs/FAQ/faq.tex
fix _

  Some features of Fortran 2003 are used, in particular, the {\tt
    ISO_C_BINDING} feature of Fortran 2003 is needed to define a long
  integer type for some MPI operations in Fortran.  This is supported
  by most Fortran compilers even if they don't support the entire
  Fortran 2003 standard.

>>>>

  Some features of Fortran 2003 are used, in particular, the {\tt
    ISO\_C\_BINDING} feature of Fortran 2003 is needed to define a long
  integer type for some MPI operations in Fortran.  This is supported
  by most Fortran compilers even if they don't support the entire
  Fortran 2003 standard.
